Spatial modelling of the electoral two-party preferred vote in Australia. A study of federal elections between 2001 and 2016 via the `eechidna` `R` package.

### 2019-03-27 01-intro.Rmd
add logs, cooksd

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = F, fig.pos = 'h', fig.align = 'center', cache = T, message = F)
library(tidyverse)
library(eechidna)
library(ggplot2)
library(ggthemes)
library(knitr)
library(nlme)
library(rgeos)
library(spdep)
library(gridExtra)
library(grid)

@@

@@

>>>>

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = F, fig.pos = 'h', fig.align = 'center', cache = T, message = F)
library(tidyverse)
library(eechidna)
library(ggplot2)
library(ggthemes)
library(knitr)
library(nlme)
library(rgeos)
library(spdep)
library(gridExtra)
library(grid)
library(predictmeans)

@@

# Take log of indigneous, judaism, islam, buddhism
abs2016 <- abs2016 %>% mutate(Indigenous = log(Indigenous), Judaism = log(Judaism), Islam = log(Islam), Buddhism = log(Buddhism))
abs2013 <- abs2013 %>% mutate(Indigenous = log(Indigenous), Judaism = log(Judaism), Islam = log(Islam), Buddhism = log(Buddhism))
abs2010 <- abs2010 %>% mutate(Indigenous = log(Indigenous), Judaism = log(Judaism), Islam = log(Islam), Buddhism = log(Buddhism))
abs2007 <- abs2007 %>% mutate(Indigenous = log(Indigenous), Judaism = log(Judaism), Islam = log(Islam), Buddhism = log(Buddhism))
abs2004 <- abs2004 %>% mutate(Indigenous = log(Indigenous), Judaism = log(Judaism), Islam = log(Islam), Buddhism = log(Buddhism))
abs2001 <- abs2001 %>% mutate(Indigenous = log(Indigenous), Judaism = log(Judaism), Islam = log(Islam), Buddhism = log(Buddhism))

@@

  # Cooks distance
  #gls_model$cooksd <- unname(predictmeans::CookD(gls_model, plot = FALSE))
